---
title: "KPI Report-HQS0017-Kawakib"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(lubridate)) install.packages("lubridate", repos = "http://cran.us.r-project.org")
if(!require(bizdays)) install.packages("bizdays", repos = "http://cran.us.r-project.org")
if(!require(readxl)) install.packages("readxl", repos = "http://cran.us.r-project.org")
if(!require(googledrive)) install.packages("googledrive", repos = "http://cran.us.r-project.org")
if(!require(knitr)) install.packages("knitr", repos = "http://cran.us.r-project.org")
drive_auth(email = "3pl.hr.pnd@gmail.com")
create.calendar(name = "mycal", weekdays = c("friday","saturday"))
options(digits = 1)
dir.create(file.path(getwd(), "DATA"))

# Invoice Tracking
drive_download("Invoice Tracking", path = file.path(getwd(),"DATA","Invoice Tracking.xlsx"),overwrite = TRUE)
IT_Salary <- read_excel(file.path(getwd(),"DATA","Invoice Tracking.xlsx"),skip = 2,sheet = "Salary Invoices") %>% fill(Month)
colnames(IT_Salary) <- colnames(IT_Salary) %>% str_replace_all("2","T") %>% str_replace_all(" ","") %>% str_replace_all("-","_") %>% str_replace_all("&","n")
IT_Salary <- IT_Salary %>% gather(key = "Invoice_Recepient",value = "value",TB_KRT:RPOC) %>% spread(key = Stage, value = value)
colnames(IT_Salary) <- colnames(IT_Salary) %>% str_replace_all(" ","_")  
IT_Salary <- IT_Salary %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved) %>% 
  arrange(match(Month,month.name)) %>% mutate(Date_Prepared = as_date(as.integer(Date_Prepared), origin = "1899-12-30"), 
                                              Date_Submitted = as_date(as.integer(Date_Submitted), origin = "1899-12-30"),
                                              Date_Payment_Recieved = as_date(as.integer(Date_Payment_Recieved), origin = "1899-12-30"))

IT_FOT <- read_excel(file.path(getwd(),"DATA","Invoice Tracking.xlsx"),skip = 2,sheet = "Fixed Overtime Invoices") %>% fill(Month)
colnames(IT_FOT) <- colnames(IT_FOT) %>% str_replace_all("2","T") %>% str_replace_all(" ","") %>% str_replace_all("-","_") %>% str_replace_all("&","n")
IT_FOT <- IT_FOT %>% gather(key = "Invoice_Recepient",value = "value",TB_KRT:RPOC) %>% spread(key = Stage, value = value)
colnames(IT_FOT) <- colnames(IT_FOT) %>% str_replace_all(" ","_") 
IT_FOT <- IT_FOT %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved)
IT_FOT <- IT_FOT %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved) %>% 
  arrange(match(Month,month.name)) %>% mutate(Date_Prepared = as_date(as.integer(Date_Prepared), origin = "1899-12-30"), 
                                              Date_Submitted = as_date(as.integer(Date_Submitted), origin = "1899-12-30"),
                                              Date_Payment_Recieved = as_date(as.integer(Date_Payment_Recieved), origin = "1899-12-30"))

IT_VOT <- read_excel(file.path(getwd(),"DATA","Invoice Tracking.xlsx"),skip = 2,sheet = "Variable Overtime Invoices") %>% fill(Month)
colnames(IT_VOT) <- colnames(IT_VOT) %>% str_replace_all("2","T") %>% str_replace_all(" ","") %>% str_replace_all("-","_") %>% str_replace_all("&","n")
IT_VOT <- IT_VOT %>% gather(key = "Invoice_Recepient",value = "value",TB_KRT:RPOC) %>% spread(key = Stage, value = value)
colnames(IT_VOT) <- colnames(IT_VOT) %>% str_replace_all(" ","_") 
IT_VOT <- IT_VOT %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved)
IT_VOT <- IT_VOT %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved) %>% 
  arrange(match(Month,month.name)) %>% mutate(Date_Prepared = as_date(as.integer(Date_Prepared), origin = "1899-12-30"), 
                                              Date_Submitted = as_date(as.integer(Date_Submitted), origin = "1899-12-30"),
                                              Date_Payment_Recieved = as_date(as.integer(Date_Payment_Recieved), origin = "1899-12-30"))

IT_CL <- read_excel(file.path(getwd(),"DATA","Invoice Tracking.xlsx"),skip = 2,sheet = "Casual Labour Invoices") %>% fill(Month)
colnames(IT_CL) <- colnames(IT_CL) %>% str_replace_all("2","T") %>% str_replace_all(" ","") %>% str_replace_all("-","_") %>% str_replace_all("&","n")
IT_CL <- IT_CL %>% gather(key = "Invoice_Recepient",value = "value",TB_KRT:RPOC) %>% spread(key = Stage, value = value)
colnames(IT_CL) <- colnames(IT_CL) %>% str_replace_all(" ","_") 
IT_CL <- IT_CL %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved)
IT_CL <- IT_CL %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved) %>% 
  arrange(match(Month,month.name)) %>% mutate(Date_Prepared = as_date(as.integer(Date_Prepared), origin = "1899-12-30"), 
                                              Date_Submitted = as_date(as.integer(Date_Submitted), origin = "1899-12-30"),
                                              Date_Payment_Recieved = as_date(as.integer(Date_Payment_Recieved), origin = "1899-12-30"))

# Customer Satisfaction Survey
drive_download("Business Development Survey Data Collection", path = file.path(getwd(),"DATA","Satisfaction Survey.csv"),overwrite = TRUE)
CSS <- read_csv(file.path(getwd(),"DATA","Satisfaction Survey.csv"),skip = 8)
CSS <- CSS %>% gather(key = "Dimension", value = "Score", 3:ncol(.))
colnames(CSS) <- colnames(CSS) %>% str_replace_all(.," ","_") %>% str_replace_all(.,"-","")

# Log Sheet
drive_download("Log Sheet", path = file.path(getwd(),"DATA","Log Sheet.csv"),overwrite = TRUE)
Log_Sheet <- read_csv(file.path(getwd(),"Data","Log Sheet.csv"),skip = 5)
colnames(Log_Sheet) <- colnames(Log_Sheet) %>% str_replace_all(.," ","_") %>% str_replace_all(.,"-","")
Log_Sheet <- Log_Sheet %>% mutate(Date_Request_Prepared_by_HQ = dmy(Date_Request_Prepared_by_HQ),
                     Date_Request_Recieved_by_Staff = dmy(Date_Request_Recieved_by_Staff),
                     Date_Request_Recieved_by_Coordinator = dmy(Date_Request_Recieved_by_Coordinator))

# Sheet Collection Tracking
drive_download("Sheet Collection Tracker", path = file.path(getwd(),"DATA","Sheet Collection Tracker.xlsx"),overwrite = TRUE)
TS <- read_excel(file.path(getwd(),"DATA","Sheet Collection Tracker.xlsx"),skip = 2, sheet = "Time Sheets - KRT")
colnames(TS) <- colnames(TS) %>% str_replace_all("2","TWO")
TS <- TS %>% fill(Month)
TS <- TS %>% gather(3:ncol(.),key = "OPCO", value = "Date") %>% mutate(OPCO = str_replace_all(OPCO,"TWO","2")) %>% mutate(Date = as_datetime(Date))

OTS <- read_excel(file.path(getwd(),"DATA","Sheet Collection Tracker.xlsx"),skip = 2, sheet = "Overtime Sheets - KRT")
colnames(OTS) <- colnames(OTS) %>% str_replace_all("2","TWO")
OTS <- OTS %>% fill(Month)
OTS <- OTS %>% gather(3:ncol(.),key = "OPCO", value = "Date") %>% mutate(OPCO = str_replace_all(OPCO,"TWO","2"))  %>% mutate(Date = as_datetime(Date))

# Training Tracker
drive_download("Mandatory Training Tracker", path = file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),overwrite = TRUE)
MTT <- read_excel(file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),range = "E7:G56") %>%
  rbind(read_excel(file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),range = "I7:K56")) %>%
  rbind(read_excel(file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),range = "M7:O56")) %>% 
  cbind(read_excel(file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),range = "A7:C56")) %>% 
  mutate(Course = c(rep("Customer Service",49),rep("Conflict Resolution",49),rep("People Management",49))) %>%
  relocate(ID:Course, .before = 1) %>% filter(!is.na(ID))
colnames(MTT) <- colnames(MTT) %>% str_replace_all(.," ","_") %>% str_replace_all(.,"-","")


# Weekly meeting Attendance 
drive_download("Weekly Meeting Attendance Tracker", path = file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),overwrite = TRUE)
WMA <- read_excel(file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),skip = 6, sheet = "April - June") %>%
  cbind(read_excel(file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),skip = 6, sheet = "Jul - Sep") %>% select(4:ncol(.))) %>%
  cbind(read_excel(file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),skip = 6, sheet = "Oct - Dec") %>% select(4:ncol(.)))
colnames(WMA) <- colnames(WMA) %>% str_replace_all(.," ","_") %>% str_replace_all(.,"-","")
WMA_Legend <- read_excel(file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),skip = 1,n_max = 3, col_names = FALSE, sheet = "April - June") %>% pull(1)
WMA <- WMA %>% gather(key = "Date", value = "Attendance",4:ncol(.)) %>% filter(!is.na(ID)) %>% mutate(Date = as_date(as.integer(Date), origin = "1899-12-30"))

# Development program tracking
drive_download("Development Program Attendance", path = file.path(getwd(),"DATA","Development Program Attendance.xlsx"),overwrite = TRUE)
DPA <- read_excel(file.path(getwd(),"DATA","Development Program Attendance.xlsx"),skip = 2, sheet = "DPA")
colnames(DPA) <- colnames(DPA) %>% str_replace_all(" ","_")
DPA <- DPA %>% gather(key = "Program_Name",value = "Attendance",5:ncol(.))            

```

# Score Card

```{r score card, echo=FALSE, warning=FALSE}
# Score Card 2B Kaawakib
SC_Log_Sheet <- Log_Sheet %>% mutate(Time = bizdays(Date_Request_Recieved_by_Staff, Date_Request_Recieved_by_Coordinator,"mycal") <= 3) %>% 
  filter(Coordinator_ID == "HQS0017", Request_Type != "Insurance Issues") %>%
  summarise(`Average Time for Employee Request completion` = mean(Time, na.rm = T)) %>% 
  gather(key = "KPI", value = "Score")

SC_CSS <- CSS %>%  summarise(Score = mean(Score,na.rm = TRUE) * 25) %>% mutate(KPI = "Customer Satisfaction Score") %>% select(KPI, Score)

SC_IS <- IT_Salary %>%  mutate(Invoice_Recepient = if_else(str_detect(Invoice_Recepient,"^T"), "2B",
                                                           if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>%
  group_by(Invoice_Recepient) %>%
  mutate(Month = match(Month,month.name),
         Submit_On_time = Date_Submitted <= dmy(paste(1,match(Month,month.name) + 1,2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name) + 1,2020))) %>% 
  mutate(Day_Pay = if_else(month(Date_Payment_Recieved) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), 
                           day(Date_Payment_Recieved)),
         Day_Submit = if_else(month(Date_Submitted) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)),
                              day(Date_Submitted))) %>%
  summarise(Average_Date_Pay = mean(Day_Pay,na.rm = T),
            Average_Date_Submit = mean(Day_Submit,na.rm = T),
            Submit_On_time = mean(Submit_On_time, na.rm = T) * 100, 
            Pay_On_time = mean(Pay_On_time,na.rm = T) * 100) %>% 
  gather(key = "KPI", value = "Score", 2:5) %>%
  filter(Invoice_Recepient == "2B") %>% select(2:3) %>% 
  mutate(KPI = c("Average Date Salary Payment Recieved","Average Date Salary Invoices submitted on",
                 "Salary Invoices submitted on time","Salary Payments Submitted on time"))

SC_CL <- IT_CL %>% mutate(Invoice_Recepient = if_else(str_detect(Invoice_Recepient,"^T"), "2B",
                                                           if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>%
  group_by(Invoice_Recepient) %>%
  mutate(Month = match(Month,month.name),
         Submit_On_time = Date_Submitted <= dmy(paste(1,match(Month,month.name) + 1,2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name) + 1,2020))) %>% 
  mutate(Day_Pay = if_else(month(Date_Payment_Recieved) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), 
                           day(Date_Payment_Recieved)),
         Day_Submit = if_else(month(Date_Submitted) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)),
                              day(Date_Submitted))) %>%
  summarise(Average_Date_Pay = mean(Day_Pay,na.rm = T),
            Average_Date_Submit = mean(Day_Submit,na.rm = T),
            Submit_On_time = mean(Submit_On_time, na.rm = T) * 100, 
            Pay_On_time = mean(Pay_On_time,na.rm = T) * 100) %>% 
  gather(key = "KPI", value = "Score", 2:5) %>%
  filter(Invoice_Recepient == "2B") %>% select(2:3) %>% 
  mutate(KPI = c("Average Date Casual Labor Payment Recieved","Average Date Casual Labor Invoices submitted on",
                 "Casual Labor Invoices submitted on time","Casual Labor Payments Submitted on time"))

SC_IFO <- IT_FOT %>% mutate(Invoice_Recepient = if_else(str_detect(Invoice_Recepient,"^T"), "2B",
                                                           if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>%
  group_by(Invoice_Recepient) %>%
  mutate(Month = match(Month,month.name),
         Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name) + 1,2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(25,match(Month,month.name) + 1,2020))) %>% 
  mutate(Day_Pay = if_else(month(Date_Payment_Recieved) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), 
                           day(Date_Payment_Recieved)),
         Day_Submit = if_else(month(Date_Submitted) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)),
                              day(Date_Submitted))) %>%
  summarise(Average_Date_Pay = mean(Day_Pay,na.rm = T),
            Average_Date_Submit = mean(Day_Submit,na.rm = T),
            Submit_On_time = mean(Submit_On_time, na.rm = T) * 100, 
            Pay_On_time = mean(Pay_On_time,na.rm = T) * 100) %>% 
  gather(key = "KPI", value = "Score", 2:5) %>%
  filter(Invoice_Recepient == "2B") %>% select(2:3) %>% 
  mutate(KPI = c("Average Date Fixed Overtime Payment Recieved","Average Date Fixed Overtime Invoices submitted on",
                 "Casual Fixed Overtime submitted on time","Casual Fixed Overtime Submitted on time"))

SC_IVO <- IT_VOT %>% mutate(Invoice_Recepient = if_else(str_detect(Invoice_Recepient,"^T"), "2B",
                                                           if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>%
  group_by(Invoice_Recepient) %>%
  mutate(Month = match(Month,month.name),
         Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name) + 1,2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(25,match(Month,month.name) + 1,2020))) %>% 
  mutate(Day_Pay = if_else(month(Date_Payment_Recieved) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), 
                           day(Date_Payment_Recieved)),
         Day_Submit = if_else(month(Date_Submitted) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)),
                              day(Date_Submitted))) %>%
  summarise(Average_Date_Pay = mean(Day_Pay,na.rm = T),
            Average_Date_Submit = mean(Day_Submit,na.rm = T),
            Submit_On_time = mean(Submit_On_time, na.rm = T) * 100, 
            Pay_On_time = mean(Pay_On_time,na.rm = T) * 100) %>% 
  gather(key = "KPI", value = "Score", 2:5) %>%
  filter(Invoice_Recepient == "2B") %>% select(2:3) %>% 
  mutate(KPI = c("Average Date Variable Overtime Payment Recieved","Average Date Variable Overtime Invoices submitted on",
                 "Casual Variable Overtime submitted on time","Casual Variable Overtime Submitted on time"))


SC_WMA <- WMA %>% group_by(ID) %>% summarise(Score = mean(Attendance == "P", na.rm = T) * 100) %>% 
  filter(ID == "HQS0017") %>% mutate(KPI = "Weekly Meeting Attendance") %>% select(KPI,Score)

SC_MTT <- MTT %>% summarise(Mandatory_Training_Score = mean(Score,na.rm = T), Mandatory_Training_Attendance = mean(!is.na(Date_Completed),na.rm = T) * 100) %>% 
  gather(key = "KPI", value = "Score") %>% mutate(KPI = str_replace_all(KPI,"_"," "))


SC_TS <- TS %>% filter(Stage == "Date Submitted to the Office") %>% group_by(OPCO) %>% mutate(Month = match(Month,month.name)) %>%
  mutate(Success = Date <= following(dmy(paste(15,Month + 1,2020)),cal = "mycal")) %>%
  mutate(Date = if_else(month(Date) > Month + 1,day(ceiling_date(dmy(paste(1,Month,2020, sep = "/")), "month") - 1),day(Date))) %>%
  summarise(Day = mean(Date, na.rm = T), Success = mean(Success,na.rm =T) * 100) %>% 
  filter(OPCO == "2B") %>%
  gather(2:3,key = "KPI",value = "Score") %>% 
  mutate(KPI = c("Average Date Time Sheets submitted on","Time Sheets Submitted on Time")) %>% select(-1)

SC_OTS <- OTS %>% filter(Stage == "Date Submitted to the Office") %>% group_by(OPCO) %>% mutate(Month = match(Month,month.name)) %>%
  mutate(Success = Date <= following(dmy(paste(15,Month + 1,2020)),cal = "mycal")) %>%
  mutate(Date = if_else(month(Date) > Month + 1,day(ceiling_date(dmy(paste(1,Month,2020, sep = "/")), "month") - 1),day(Date))) %>%
  summarise(Day = mean(Date, na.rm = T), Success = mean(Success,na.rm =T) * 100) %>% 
  filter(OPCO == "2B") %>%
  gather(2:3,key = "KPI",value = "Score") %>% 
  mutate(KPI = c("Average Date Time Sheets submitted on","Time Sheets Submitted on Time")) %>% select(-1)

SC_DPA <- DPA %>% group_by(ID) %>% summarise(Score = sum(Attendance == "Attended",na.rm = T)) %>% filter(ID == "HQS0017") %>%
  mutate(KPI = "Development Programs Attended") %>% select(KPI, Score)


SC <- SC_Log_Sheet %>% rbind(SC_CSS) %>% rbind(SC_IS) %>% rbind(SC_IFO) %>% 
  rbind(SC_IVO) %>% rbind(SC_CL) %>%
  rbind(SC_WMA) %>% rbind(SC_MTT) %>% rbind(SC_TS) %>% rbind(SC_OTS) %>% rbind(SC_DPA)
SC_units <- c(" day",
              "%",
              " day"," day","%","%",
              " day"," day","%","%",
              " day"," day","%","%",
              " day"," day","%","%",
              "%",
              "%",
              "%",
              " day","%",
              " day","%",
              "")
SC_target <- c(3,
               85,
               1,15,80,80,
               15,25,80,80,
               15,25,80,80,
               1,15,80,80,
               80,
               80,
               100,
               15,80,
               15,80,
               1)
SC %>% mutate(Score = format(Score, digits = 0), Target = SC_target, 
              Units = SC_units, Units = if_else(str_detect(Units," day"),
                                                if_else(str_detect(Score,"\\d*1$"),"st",
                                                        if_else(str_detect(Score,"\\d*2$"),"nd",
                                                                if_else(str_detect(Score,"\\d*13$"),"th",
                                                                        if_else(str_detect(Score,"3$"),"rd","th")))),Units),
              Score = paste(Score,Units,sep = ""), 
              Units = SC_units, Units = if_else(str_detect(Units," day"),
                                                if_else(str_detect(Target,"\\d*1$"),"st",
                                                        if_else(str_detect(Target,"\\d*2$"),"nd",
                                                                if_else(str_detect(Target,"\\d*13$"),"th",
                                                                        if_else(str_detect(Target,"3$"),"rd","th")))),Units),
              Target = paste(Target,Units,sep = "")) %>% select(-Units) %>% kable()

```

# Detailed Analysis

## Invoice Collection and Submission

### Salary Invoices: Date Submitted, Date Payment Collected

```{r Salary Invoice Date Submitted, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
## Salary Invoices
### Date Submitted
IT_Salary %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Month = match(Month,month.name), 
         Date_Pay = if_else(month(Date_Payment_Recieved) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), day(Date_Payment_Recieved)),
         Date_Submit = if_else(month(Date_Submitted) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), day(Date_Submitted))) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>%  
  group_by(OPCO,Month) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  ungroup() %>% 
  gather(key = "KPI", value = "Day", Date_Pay:Date_Submit) %>%
  mutate(KPI = if_else(KPI == "Date_Pay","Average Date Salary Payment Recieved","Average Date Salary Invoices submitted on"),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>%
  select(Month,Invoice_Recepient,KPI,Day, -OPCO) %>%
  ggplot(aes(Month,Day,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + 
  geom_hline(yintercept = c(1,15), linetype = 2) +
  labs(y = "Date Submitted", title = "Salary Invoices")  +
  scale_y_continuous(limits = c(0,30), expand = c(0,NA), breaks = seq(0,31,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Fixed Overtime Invoices: Date Submitted, Date Payment Collected

```{r FOT Invoice Date Submitted, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
### Date Submitted
IT_FOT %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Month = match(Month,month.name), 
         Date_Pay = if_else(month(Date_Payment_Recieved) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), day(Date_Payment_Recieved)),
         Date_Submit = if_else(month(Date_Submitted) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), day(Date_Submitted))) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>%  
  group_by(OPCO,Month) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  ungroup() %>% 
  gather(key = "KPI", value = "Day", Date_Pay:Date_Submit) %>%
  mutate(KPI = if_else(KPI == "Date_Pay","Average Date Salary Payment Recieved","Average Date Salary Invoices submitted on"),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>%
  select(Month,Invoice_Recepient,KPI,Day, -OPCO) %>%
  ggplot(aes(Month,Day,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + 
  geom_hline(yintercept = c(15,25), linetype = 2) +
  labs(y = "Date Submitted", title = "Fixed Overtime Invoices")  +
  scale_y_continuous(limits = c(0,30), expand = c(0,NA), breaks = seq(0,31,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Variable Overtime Invoices: Date Submitted, Date Payment Collected

```{r VOT Invoice Date Submitted, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
### Date Submitted
IT_VOT %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Month = match(Month,month.name), 
         Date_Pay = if_else(month(Date_Payment_Recieved) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), day(Date_Payment_Recieved)),
         Date_Submit = if_else(month(Date_Submitted) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), day(Date_Submitted))) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>%  
  group_by(OPCO,Month) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  ungroup() %>% 
  gather(key = "KPI", value = "Day", Date_Pay:Date_Submit) %>%
  mutate(KPI = if_else(KPI == "Date_Pay","Average Date Salary Payment Recieved","Average Date Salary Invoices submitted on"),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>%
  select(Month,Invoice_Recepient,KPI,Day, -OPCO) %>%
  ggplot(aes(Month,Day,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + 
  geom_hline(yintercept = c(15,25), linetype = 2) +
  labs(y = "Date Submitted", title = "Variable Overtime Invoices")  +
  scale_y_continuous(limits = c(0,30), expand = c(0,NA), breaks = seq(0,31,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Casual Labour Invoices: Date Submitted, Date Payment Collected

```{r Casual Invoice Date Submitted, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
### Date Submitted
IT_CL %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Month = match(Month,month.name), 
         Date_Pay = if_else(month(Date_Payment_Recieved) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), day(Date_Payment_Recieved)),
         Date_Submit = if_else(month(Date_Submitted) > Month + 1, day(ceiling_date(dmy(paste(1,Month + 1,2020,sep = "/")) -1)), day(Date_Submitted))) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>%  
  group_by(OPCO,Month) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  ungroup() %>% 
  gather(key = "KPI", value = "Day", Date_Pay:Date_Submit) %>%
  mutate(KPI = if_else(KPI == "Date_Pay","Average Date Salary Payment Recieved","Average Date Salary Invoices submitted on"),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>%
  select(Month,Invoice_Recepient,KPI,Day, -OPCO) %>%
  ggplot(aes(Month,Day,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + 
  geom_hline(yintercept = c(1,15), linetype = 2) +
  labs(y = "Date Submitted", title = "Casual Labor Invoices")  +
  scale_y_continuous(limits = c(0,30), expand = c(0,NA), breaks = seq(0,31,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```


## Customer Service Survey

```{r CSS Details, echo=FALSE, message=FALSE, warning=FALSE}
CSS %>%  group_by(Dimension,OPCO) %>% summarise(Score = mean(Score) * 25) %>% mutate(KPI = Dimension, Quarter = "3rd")  %>% ungroup() %>% filter(OPCO == "2B") %>%
  select(Quarter, KPI, Score)  %>% kable()
```

## Time Sheets

### Date Submitted

```{r Time Sheet Submission, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
## Time Sheet collection
TS %>% filter(Stage == "Date Submitted to the Office") %>% 
  filter(OPCO == "2B") %>% 
  mutate(Month = match(Month,month.name), Sheet = "Time Sheet") %>% 
  rbind(
    OTS %>% filter(Stage == "Date Submitted to the Office") %>% 
      filter(OPCO == "2B") %>% 
      mutate(Month = match(Month,month.name), Sheet = "Overtime Sheet")
  ) %>% 
  mutate(Day = if_else(month(Date) > Month + 1,day(ceiling_date(dmy(paste(1,Month,2020, sep = "/")), "month") - 1),day(Date))) %>%
  ggplot(aes(Month,Day, color = Sheet)) + geom_point() + 
  geom_hline(yintercept = c(20,15), linetype = 2, color = c("red","blue")) +
  labs(title = "Date Sheets Submitted to HQ")  +
  scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  scale_y_continuous(limits = c(1,31), breaks = c(1,seq(5,31,5))) +
  theme(plot.title = element_text(hjust = 0.5))

```

## Staff Requests

```{r staff requests details, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
# Log Sheet Details
Log_Sheet %>% mutate(Month = month(Date_Request_Recieved_by_Coordinator), 
                     Time = bizdays(Date_Request_Recieved_by_Staff, Date_Request_Recieved_by_Coordinator,"mycal")) %>% 
  filter(Coordinator_ID == "HQS0017", Request_Type != "Insurance Issues") %>% group_by(Request_Type,Month) %>% 
  summarise(Time = mean(Time,na.rm = T)) %>%
  ggplot(aes(Month,Time, color = Request_Type)) + geom_point() + 
  labs(title = "Time to Complete Employee Requests", color = "Request Type", y = "Days") +
  scale_x_continuous(limits = c(4,12), labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

## Mandatory Training

```{r MTT details, echo=FALSE, message=FALSE, warning=FALSE}
MTT %>% filter(ID == "HQS0017") %>% mutate(Completion_Status = if_else(is.na(Date_Completed), "Not Completed","Completed"), 
                                           Score = paste(Score,"/5",sep = "")) %>% 
  select(Course, Completion_Status, Score) %>% kable(col.names = c("Course","Completion Status","Score"))
```

## Weekly Meeting Attendance

```{r WMA details, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
WMA %>% filter(ID == "HQS0017") %>% mutate(Month = month(Date)) %>% group_by(Month, Attendance) %>% 
  filter(Date <= Sys.Date() & Date > dmy("16/07/2020")) %>%
  summarise(n= n()) %>% 
  ggplot(aes(Month,n, fill = Attendance)) + geom_bar(stat = "identity", position = "dodge", color = "black") + 
  scale_x_continuous(limits = c(4,12), breaks = 4:12, labels = month.abb[4:12]) + 
  scale_y_continuous(limits = c(0,5), expand = c(0,NA)) + 
  labs(y = "Days", title = "Weekly Meeting Attendance", fill = "Legend") + 
  theme(plot.title = element_text(hjust = 0.5))
```

## Development Program Attendance

No Details about the Development Program