---
title: "KPI Report-HQS0017-Kawakib"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(lubridate)) install.packages("lubridate", repos = "http://cran.us.r-project.org")
if(!require(bizdays)) install.packages("bizdays", repos = "http://cran.us.r-project.org")
if(!require(readxl)) install.packages("readxl", repos = "http://cran.us.r-project.org")
if(!require(googledrive)) install.packages("googledrive", repos = "http://cran.us.r-project.org")
if(!require(knitr)) install.packages("knitr", repos = "http://cran.us.r-project.org")
drive_auth(email = "3pl.hr.pnd@gmail.com")
create.calendar(name = "mycal", weekdays = c("friday","saturday"))
options(digits = 1)
dir.create(file.path(getwd(), "DATA"))

# Invoice Tracking
drive_download("Invoice Tracking", path = file.path(getwd(),"DATA","Invoice Tracking.xlsx"),overwrite = TRUE)
IT_Salary <- read_excel(file.path(getwd(),"DATA","Invoice Tracking.xlsx"),skip = 2,sheet = "Salary Invoices") %>% fill(Month)
colnames(IT_Salary) <- colnames(IT_Salary) %>% str_replace_all("2","T") %>% str_replace_all(" ","") %>% str_replace_all("-","_") %>% str_replace_all("&","n")
IT_Salary <- IT_Salary %>% gather(key = "Invoice_Recepient",value = "value",TB_KRT:RPOC) %>% spread(key = Stage, value = value)
colnames(IT_Salary) <- colnames(IT_Salary) %>% str_replace_all(" ","_")  
IT_Salary <- IT_Salary %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved) %>% 
  arrange(match(Month,month.name)) %>% mutate(Date_Prepared = as_date(as.integer(Date_Prepared), origin = "1899-12-30"), 
                                              Date_Submitted = as_date(as.integer(Date_Submitted), origin = "1899-12-30"),
                                              Date_Payment_Recieved = as_date(as.integer(Date_Payment_Recieved), origin = "1899-12-30"))

IT_FOT <- read_excel(file.path(getwd(),"DATA","Invoice Tracking.xlsx"),skip = 2,sheet = "Fixed Overtime Invoices") %>% fill(Month)
colnames(IT_FOT) <- colnames(IT_FOT) %>% str_replace_all("2","T") %>% str_replace_all(" ","") %>% str_replace_all("-","_") %>% str_replace_all("&","n")
IT_FOT <- IT_FOT %>% gather(key = "Invoice_Recepient",value = "value",TB_KRT:RPOC) %>% spread(key = Stage, value = value)
colnames(IT_FOT) <- colnames(IT_FOT) %>% str_replace_all(" ","_") 
IT_FOT <- IT_FOT %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved)
IT_FOT <- IT_FOT %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved) %>% 
  arrange(match(Month,month.name)) %>% mutate(Date_Prepared = as_date(as.integer(Date_Prepared), origin = "1899-12-30"), 
                                              Date_Submitted = as_date(as.integer(Date_Submitted), origin = "1899-12-30"),
                                              Date_Payment_Recieved = as_date(as.integer(Date_Payment_Recieved), origin = "1899-12-30"))

IT_VOT <- read_excel(file.path(getwd(),"DATA","Invoice Tracking.xlsx"),skip = 2,sheet = "Variable Overtime Invoices") %>% fill(Month)
colnames(IT_VOT) <- colnames(IT_VOT) %>% str_replace_all("2","T") %>% str_replace_all(" ","") %>% str_replace_all("-","_") %>% str_replace_all("&","n")
IT_VOT <- IT_VOT %>% gather(key = "Invoice_Recepient",value = "value",TB_KRT:RPOC) %>% spread(key = Stage, value = value)
colnames(IT_VOT) <- colnames(IT_VOT) %>% str_replace_all(" ","_") 
IT_VOT <- IT_VOT %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved)
IT_VOT <- IT_VOT %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved) %>% 
  arrange(match(Month,month.name)) %>% mutate(Date_Prepared = as_date(as.integer(Date_Prepared), origin = "1899-12-30"), 
                                              Date_Submitted = as_date(as.integer(Date_Submitted), origin = "1899-12-30"),
                                              Date_Payment_Recieved = as_date(as.integer(Date_Payment_Recieved), origin = "1899-12-30"))

IT_CL <- read_excel(file.path(getwd(),"DATA","Invoice Tracking.xlsx"),skip = 2,sheet = "Casual Labour Invoices") %>% fill(Month)
colnames(IT_CL) <- colnames(IT_CL) %>% str_replace_all("2","T") %>% str_replace_all(" ","") %>% str_replace_all("-","_") %>% str_replace_all("&","n")
IT_CL <- IT_CL %>% gather(key = "Invoice_Recepient",value = "value",TB_KRT:RPOC) %>% spread(key = Stage, value = value)
colnames(IT_CL) <- colnames(IT_CL) %>% str_replace_all(" ","_") 
IT_CL <- IT_CL %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved)
IT_CL <- IT_CL %>% select(Month,Invoice_Recepient, Invoice_No., Date_Prepared, Date_Submitted, Date_Payment_Recieved) %>% 
  arrange(match(Month,month.name)) %>% mutate(Date_Prepared = as_date(as.integer(Date_Prepared), origin = "1899-12-30"), 
                                              Date_Submitted = as_date(as.integer(Date_Submitted), origin = "1899-12-30"),
                                              Date_Payment_Recieved = as_date(as.integer(Date_Payment_Recieved), origin = "1899-12-30"))

# Customer Satisfaction Survey
drive_download("Business Development Survey Data Collection", path = file.path(getwd(),"DATA","Satisfaction Survey.csv"),overwrite = TRUE)
CSS <- read_csv(file.path(getwd(),"DATA","Satisfaction Survey.csv"),skip = 8)
CSS <- CSS %>% gather(key = "Dimension", value = "Score", 3:ncol(.))
colnames(CSS) <- colnames(CSS) %>% str_replace_all(.," ","_") %>% str_replace_all(.,"-","")

# Log Sheet
drive_download("Log Sheet", path = file.path(getwd(),"DATA","Log Sheet.csv"),overwrite = TRUE)
Log_Sheet <- read_csv(file.path(getwd(),"Data","Log Sheet.csv"),skip = 5)
colnames(Log_Sheet) <- colnames(Log_Sheet) %>% str_replace_all(.," ","_") %>% str_replace_all(.,"-","")
Log_Sheet <- Log_Sheet %>% mutate(Date_Request_Prepared_by_HQ = dmy(Date_Request_Prepared_by_HQ),
                     Date_Request_Recieved_by_Staff = dmy(Date_Request_Recieved_by_Staff),
                     Date_Request_Recieved_by_Coordinator = dmy(Date_Request_Recieved_by_Coordinator))

# Sheet Collection Tracking
drive_download("Sheet Collection Tracker", path = file.path(getwd(),"DATA","Sheet Collection Tracker.xlsx"),overwrite = TRUE)
TS <- read_excel(file.path(getwd(),"DATA","Sheet Collection Tracker.xlsx"),skip = 2, sheet = "Time Sheets - KRT")
colnames(TS) <- colnames(TS) %>% str_replace_all("2","TWO")
TS <- TS %>% fill(Month)
TS <- TS %>% gather(3:ncol(.),key = "OPCO", value = "Date")

OTS <- read_excel(file.path(getwd(),"DATA","Sheet Collection Tracker.xlsx"),skip = 2, sheet = "Overtime Sheets - KRT")
colnames(OTS) <- colnames(OTS) %>% str_replace_all("2","TWO")
OTS <- OTS %>% fill(Month)
OTS <- OTS %>% gather(3:ncol(.),key = "OPCO", value = "Date")

# Training Tracker
drive_download("Mandatory Training Tracker", path = file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),overwrite = TRUE)
MTT <- read_excel(file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),range = "E7:G56") %>%
  rbind(read_excel(file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),range = "I7:K56")) %>%
  rbind(read_excel(file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),range = "M7:O56")) %>% 
  cbind(read_excel(file.path(getwd(),"DATA","Mandatory Training Tracker.xlsx"),range = "A7:C56")) %>% 
  mutate(Course = c(rep("Customer Service",49),rep("Conflict Resolution",49),rep("People Management",49))) %>%
  relocate(ID:Course, .before = 1) %>% filter(!is.na(ID))
colnames(MTT) <- colnames(MTT) %>% str_replace_all(.," ","_") %>% str_replace_all(.,"-","")


# Weekly meeting Attendance 
drive_download("Weekly Meeting Attendance Tracker", path = file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),overwrite = TRUE)
WMA <- read_excel(file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),skip = 6, sheet = "April - June") %>%
  cbind(read_excel(file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),skip = 6, sheet = "Jul - Sep") %>% select(4:ncol(.))) %>%
  cbind(read_excel(file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),skip = 6, sheet = "Oct - Dec") %>% select(4:ncol(.)))
colnames(WMA) <- colnames(WMA) %>% str_replace_all(.," ","_") %>% str_replace_all(.,"-","")
WMA_Legend <- read_excel(file.path(getwd(),"DATA","Weekly Meeting Attendance Tracker.xlsx"),skip = 1,n_max = 3, col_names = FALSE, sheet = "April - June") %>% pull(1)
WMA <- WMA %>% gather(key = "Date", value = "Attendance",4:ncol(.)) %>% filter(!is.na(ID)) %>% mutate(Date = as_date(as.integer(Date), origin = "1899-12-30"))

# Development program tracking
drive_download("Development Program Attendance", path = file.path(getwd(),"DATA","Development Program Attendance.xlsx"),overwrite = TRUE)
DPA <- read_excel(file.path(getwd(),"DATA","Development Program Attendance.xlsx"),skip = 2, sheet = "DPA")
colnames(DPA) <- colnames(DPA) %>% str_replace_all(" ","_")
DPA <- DPA %>% gather(key = "Program_Name",value = "Attendance",5:ncol(.))            

```

# Score Card


```{r score card, echo=FALSE, warning=FALSE}
# Score Card 2B Kaawakib
SC_Log_Sheet <- Log_Sheet %>% mutate(Time = bizdays(Date_Request_Recieved_by_Staff, Date_Request_Recieved_by_Coordinator,"mycal") <= 3) %>% 
  filter(Coordinator_ID == "HQS0017", Request_Type != "Insurance Issues") %>%
  summarise(`Average Time for Employee Request completion` = mean(Time, na.rm = T)) %>% 
  gather(key = "KPI", value = "Score")

SC_CSS <- CSS %>%  summarise(Score = mean(Score) * 25) %>% mutate(KPI = "Customer Satisfaction Score") %>% select(KPI, Score)

SC_IS <- IT_Salary %>% group_by(Invoice_Recepient) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(Average_Date_Pay = c(Average_Date_Pay[1:3],mean(Average_Date_Pay[4:5]),
                              mean(Average_Date_Pay[6:9]),rep(NA,4)),
         Average_Date_Submit = c(Average_Date_Submit[1:3],mean(Average_Date_Submit[4:5]),
                                 mean(Average_Date_Submit[6:9]),rep(NA,4)),
         Submit_On_time = c(Submit_On_time[1:3],mean(Submit_On_time[4:5]),
                            mean(Submit_On_time[6:9]),rep(NA,4)),
         Pay_On_time = c(Pay_On_time[1:3],mean(Pay_On_time[4:5]),
                         mean(Pay_On_time[6:9]),rep(NA,4)),
         Invoice_Recepient = c(Invoice_Recepient[1:3],"SHARIF","TWOB",rep(NA,4))) %>% head(5) %>%
  gather(key = "KPI", value = "Score", 2:5) %>%
  filter(Invoice_Recepient == "TWOB") %>% select(2:3) %>% 
  mutate(KPI = c("Average Date Salary Payment Recieved","Average Date Salary Invoices submitted on",
                 "Salary Invoices submitted on time","Salary Payments Submitted on time"))

SC_IS <- IT_CL %>% group_by(Invoice_Recepient) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(Average_Date_Pay = c(Average_Date_Pay[1:3],mean(Average_Date_Pay[4:5]),
                              mean(Average_Date_Pay[6:9]),rep(NA,4)),
         Average_Date_Submit = c(Average_Date_Submit[1:3],mean(Average_Date_Submit[4:5]),
                                 mean(Average_Date_Submit[6:9]),rep(NA,4)),
         Submit_On_time = c(Submit_On_time[1:3],mean(Submit_On_time[4:5]),
                            mean(Submit_On_time[6:9]),rep(NA,4)),
         Pay_On_time = c(Pay_On_time[1:3],mean(Pay_On_time[4:5]),
                         mean(Pay_On_time[6:9]),rep(NA,4)),
         Invoice_Recepient = c(Invoice_Recepient[1:3],"SHARIF","TWOB",rep(NA,4))) %>% head(5) %>%
  gather(key = "KPI", value = "Score", 2:5) %>%
  filter(Invoice_Recepient == "TWOB") %>% select(2:3) %>% 
  mutate(KPI = c("Average Date Salary Payment Recieved","Average Date Salary Invoices submitted on",
                 "Salary Invoices submitted on time","Salary Payments Submitted on time")) %>% 
  full_join(SC_IS) %>% group_by(KPI) %>% summarise(Score = mean(Score))

SC_IO <- IT_FOT %>% group_by(Invoice_Recepient) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(25,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(Average_Date_Pay = c(Average_Date_Pay[1:3],mean(Average_Date_Pay[4:5]),
                              mean(Average_Date_Pay[6:9]),rep(NA,4)),
         Average_Date_Submit = c(Average_Date_Submit[1:3],mean(Average_Date_Submit[4:5]),
                                 mean(Average_Date_Submit[6:9]),rep(NA,4)),
         Submit_On_time = c(Submit_On_time[1:3],mean(Submit_On_time[4:5]),
                            mean(Submit_On_time[6:9]),rep(NA,4)),
         Pay_On_time = c(Pay_On_time[1:3],mean(Pay_On_time[4:5]),
                         mean(Pay_On_time[6:9]),rep(NA,4)),
         Invoice_Recepient = c(Invoice_Recepient[1:3],"SHARIF","TWOB",rep(NA,4))) %>% head(5) %>%
  gather(key = "KPI", value = "Score", 2:5) %>%
  filter(Invoice_Recepient == "TWOB") %>% select(2:3) %>% 
  mutate(KPI = c("Average Date Overtime Payment Recieved","Average Date Overtime Invoices submitted on",
                 "Overtime Invoices submitted on time","Overtime Payments Submitted on time"))

SC_IO <- IT_VOT %>% group_by(Invoice_Recepient) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(25,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(Average_Date_Pay = c(Average_Date_Pay[1:3],mean(Average_Date_Pay[4:5]),
                              mean(Average_Date_Pay[6:9]),rep(NA,4)),
         Average_Date_Submit = c(Average_Date_Submit[1:3],mean(Average_Date_Submit[4:5]),
                                 mean(Average_Date_Submit[6:9]),rep(NA,4)),
         Submit_On_time = c(Submit_On_time[1:3],mean(Submit_On_time[4:5]),
                            mean(Submit_On_time[6:9]),rep(NA,4)),
         Pay_On_time = c(Pay_On_time[1:3],mean(Pay_On_time[4:5]),
                         mean(Pay_On_time[6:9]),rep(NA,4)),
         Invoice_Recepient = c(Invoice_Recepient[1:3],"SHARIF","TWOB",rep(NA,4))) %>% head(5) %>%
  gather(key = "KPI", value = "Score", 2:5) %>%
  filter(Invoice_Recepient == "TWOB") %>% select(2:3) %>% 
  mutate(KPI = c("Average Date Overtime Payment Recieved","Average Date Overtime Invoices submitted on",
                 "Overtime Invoices submitted on time","Overtime Payments Submitted on time")) %>% 
  full_join(SC_IO) %>% group_by(KPI) %>% summarise(Score = mean(Score))

SC_WMA <- WMA %>% group_by(ID) %>% summarise(Score = mean(Attendance == "P") * 100) %>% 
  filter(ID == "HQS0017") %>% mutate(KPI = "Weekly Meeting Attendance") %>% select(KPI,Score)

SC_MTT <- MTT %>% summarise(Mandatory_Training_Score = mean(Score,na.rm = T), Mandatory_Training_Attendance = mean(!is.na(Date_Completed)) * 100) %>% 
  gather(key = "KPI", value = "Score") %>% mutate(KPI = str_replace_all(KPI,"_"," "))


SC_TS <- TS %>% filter(Stage == "Date Submitted to the Office") %>% group_by(OPCO) %>% 
  mutate(Success = Date <= following(dmy(paste(15,match(Month,month.name),2020)),cal = "mycal")) %>%
  summarise(Date = day(mean.Date(Date)), Success = mean(Success) * 100) %>% 
  filter(OPCO == "TWOB") %>%
  gather(2:3,key = "KPI",value = "Score") %>% 
  mutate(KPI = c("Average Date Time Sheets submitted on","Time Sheets Submitted on Time")) %>% select(-1)

SC_OTS <- OTS %>% filter(Stage == "Date Submitted to the Office") %>% group_by(OPCO) %>% 
  mutate(Success = Date <= following(dmy(paste(15,match(Month,month.name),2020)),cal = "mycal")) %>%
  summarise(Date = day(mean.Date(Date)), Success = mean(Success) * 100) %>% 
  filter(OPCO == "TWOB") %>%
  gather(2:3,key = "KPI",value = "Score") %>% 
  mutate(KPI = c("Average Date Overtime sheets submitted on","Overtime Sheets Submitted on Time")) %>% select(-1)

SC_DPA <- DPA %>% group_by(ID) %>% summarise(Score = sum(Attendance == "Attended")) %>% filter(ID == "HQS0017") %>%
  mutate(KPI = "Development Programs Attended") %>% select(KPI, Score)


SC <- SC_Log_Sheet %>% rbind(SC_CSS) %>% rbind(SC_IS) %>% rbind(SC_IO) %>% rbind(SC_WMA) %>% rbind(SC_MTT) %>% rbind(SC_TS) %>% rbind(SC_OTS) %>% rbind(SC_DPA)
SC_units <- c(" day",
              "%",
              " day"," day","%","%",
              " day"," day","%","%",
              "%",
              "%",
              "%",
              " day","%",
              " day","%",
              "")
SC_target <- c(3,
               85,
               1,15,80,80,
               15,25,80,80,
               80,
               80,
               100,
               15,80,
               15,80,
               1)
SC %>% mutate(Score = format(Score, digits = 0), Target = SC_target, 
              Units = SC_units, Units = if_else(str_detect(Units," day"),
                                                if_else(str_detect(Score,"\\d*1$"),"st",
                                                        if_else(str_detect(Score,"\\d*2$"),"nd",
                                                                if_else(str_detect(Score,"\\d*13$"),"th",
                                                                        if_else(str_detect(Score,"3$"),"rd","th")))),Units),
              Score = paste(Score,Units,sep = ""), 
              Units = SC_units, Units = if_else(str_detect(Units," day"),
                                                if_else(str_detect(Target,"\\d*1$"),"st",
                                                        if_else(str_detect(Target,"\\d*2$"),"nd",
                                                                if_else(str_detect(Target,"\\d*13$"),"th",
                                                                        if_else(str_detect(Target,"3$"),"rd","th")))),Units),
              Target = paste(Target,Units,sep = "")) %>% select(-Units) %>% kable()

```

# Detailed Analysis

## Invoice Collection and Submission

### Salary Invoices: Date Submitted, Date Payment Collected

```{r Salary Invoice Date Submitted, echo=FALSE, message=FALSE, warning=FALSE}
## Salary Invoices
### Date Submitted
IT_Salary %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>% 
  group_by(OPCO,Month) %>%
  gather(key = "KPI", value = "Score", Average_Date_Pay:Pay_On_time) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  mutate(KPI = if_else(KPI == "Average_Date_Pay","Average Date Salary Payment Recieved",
                       if_else(KPI == "Average_Date_Submit","Average Date Salary Invoices submitted on",
                               if_else(KPI == "Submit_On_time" ,"Salary Invoices submitted on time", "Salary Payments Submitted on time"))),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>% 
  ungroup() %>%
  filter(str_detect(KPI,"Date")) %>% 
  select(Month,Invoice_Recepient,KPI,Score, -OPCO) %>% mutate(Month = match(Month,month.name)) %>% 
  ggplot(aes(Month,Score,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + labs(y = "Average Date", title = "Salary Invoices", color = "Division")  +
  scale_y_continuous(limits = c(0,31), expand = c(0,NA), breaks = seq(0,31,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Salary Invoices: Percentage Submitted on  time, Percentage Payment Collected on time

```{r Salary Invoice Percentage, echo=FALSE, message=FALSE, warning=FALSE}
### Percentage Submitted on Time
IT_Salary %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>% 
  group_by(OPCO,Month) %>%
  gather(key = "KPI", value = "Score", Average_Date_Pay:Pay_On_time) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  mutate(KPI = if_else(KPI == "Average_Date_Pay","Average Date Salary Payment Recieved",
                       if_else(KPI == "Average_Date_Submit","Average Date Salary Invoices submitted on",
                               if_else(KPI == "Submit_On_time" ,"Salary Invoices submitted on time", "Salary Payments Submitted on time"))),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>% 
  ungroup() %>%
  filter(str_detect(KPI,"on time")) %>% 
  select(Month,Invoice_Recepient,KPI,Score, -OPCO) %>% mutate(Month = match(Month,month.name), Score = cummean(Score)) %>% 
  ggplot(aes(Month,Score,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + labs(y = "Percentage On Time", title = "Salary Invoices", color = "Division")  +
  scale_y_continuous(limits = c(0,100), expand = c(0,NA), breaks = seq(0,100,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Fixed Overtime Invoices: Date Submitted, Date Payment Collected

```{r FOT Invoice Date Submitted, echo=FALSE, message=FALSE, warning=FALSE}
### Date Submitted
IT_FOT %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>% 
  group_by(OPCO,Month) %>%
  gather(key = "KPI", value = "Score", Average_Date_Pay:Pay_On_time) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  mutate(KPI = if_else(KPI == "Average_Date_Pay","Average Date Salary Payment Recieved",
                       if_else(KPI == "Average_Date_Submit","Average Date Salary Invoices submitted on",
                               if_else(KPI == "Submit_On_time" ,"Salary Invoices submitted on time", "Salary Payments Submitted on time"))),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>% 
  ungroup() %>%
  filter(str_detect(KPI,"Date")) %>% 
  select(Month,Invoice_Recepient,KPI,Score, -OPCO) %>% mutate(Month = match(Month,month.name)) %>% 
  ggplot(aes(Month,Score,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + labs(y = "Average Date", title = "Salary Invoices", color = "Division")  +
  scale_y_continuous(limits = c(0,31), expand = c(0,NA), breaks = seq(0,31,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Fixed Overtime Invoices: Percentage Submitted on  time, Percentage Payment Collected on time

```{r FOT Percentage, echo=FALSE, message=FALSE, warning=FALSE}
### Percentage Submitted on Time
IT_FOT %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>% 
  group_by(OPCO,Month) %>%
  gather(key = "KPI", value = "Score", Average_Date_Pay:Pay_On_time) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  mutate(KPI = if_else(KPI == "Average_Date_Pay","Average Date Salary Payment Recieved",
                       if_else(KPI == "Average_Date_Submit","Average Date Salary Invoices submitted on",
                               if_else(KPI == "Submit_On_time" ,"Salary Invoices submitted on time", "Salary Payments Submitted on time"))),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>% 
  ungroup() %>%
  filter(str_detect(KPI,"on time")) %>% 
  select(Month,Invoice_Recepient,KPI,Score, -OPCO) %>% mutate(Month = match(Month,month.name), Score = cummean(Score)) %>% 
  ggplot(aes(Month,Score,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + labs(y = "Percentage Submitted On Time", title = "Salary Invoices", color = "Division")  +
  scale_y_continuous(limits = c(0,100), expand = c(0,NA), breaks = seq(0,100,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Variable Overtime Invoices: Date Submitted, Date Payment Collected

```{r VOT Invoice Date Submitted, echo=FALSE, message=FALSE, warning=FALSE}
### Date Submitted
IT_VOT %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>% 
  group_by(OPCO,Month) %>%
  gather(key = "KPI", value = "Score", Average_Date_Pay:Pay_On_time) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  mutate(KPI = if_else(KPI == "Average_Date_Pay","Average Date Salary Payment Recieved",
                       if_else(KPI == "Average_Date_Submit","Average Date Salary Invoices submitted on",
                               if_else(KPI == "Submit_On_time" ,"Salary Invoices submitted on time", "Salary Payments Submitted on time"))),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>% 
  ungroup() %>%
  filter(str_detect(KPI,"Date")) %>% 
  select(Month,Invoice_Recepient,KPI,Score, -OPCO) %>% mutate(Month = match(Month,month.name)) %>% 
  ggplot(aes(Month,Score,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + labs(y = "Average Date", title = "Salary Invoices", color = "Division")  +
  scale_y_continuous(limits = c(0,31), expand = c(0,NA), breaks = seq(0,31,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Fixed Overtime Invoices: Percentage Submitted on  time, Percentage Payment Collected on time

```{r VOT Percentage, echo=FALSE, message=FALSE, warning=FALSE}
### Percentage Submitted on Time
IT_VOT %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>% 
  group_by(OPCO,Month) %>%
  gather(key = "KPI", value = "Score", Average_Date_Pay:Pay_On_time) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  mutate(KPI = if_else(KPI == "Average_Date_Pay","Average Date Salary Payment Recieved",
                       if_else(KPI == "Average_Date_Submit","Average Date Salary Invoices submitted on",
                               if_else(KPI == "Submit_On_time" ,"Salary Invoices submitted on time", "Salary Payments Submitted on time"))),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>% 
  ungroup() %>%
  filter(str_detect(KPI,"on time")) %>% 
  select(Month,Invoice_Recepient,KPI,Score, -OPCO) %>% mutate(Month = match(Month,month.name), Score = cummean(Score)) %>% 
  ggplot(aes(Month,Score,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + labs(y = "Percentage Submitted On Time", title = "Salary Invoices", colors = "Division")  +
  scale_y_continuous(limits = c(0,100), expand = c(0,NA), breaks = seq(0,100,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Casual Labour Invoices: Date Submitted, Date Payment Collected

```{r Casual Invoice Date Submitted, echo=FALSE, message=FALSE, warning=FALSE}
### Date Submitted
IT_CL %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>% 
  group_by(OPCO,Month) %>%
  gather(key = "KPI", value = "Score", Average_Date_Pay:Pay_On_time) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  mutate(KPI = if_else(KPI == "Average_Date_Pay","Average Date Salary Payment Recieved",
                       if_else(KPI == "Average_Date_Submit","Average Date Salary Invoices submitted on",
                               if_else(KPI == "Submit_On_time" ,"Salary Invoices submitted on time", "Salary Payments Submitted on time"))),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>% 
  ungroup() %>%
  filter(str_detect(KPI,"Date")) %>% 
  select(Month,Invoice_Recepient,KPI,Score, -OPCO) %>% mutate(Month = match(Month,month.name)) %>% 
  ggplot(aes(Month,Score,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + labs(y = "Average Date", title = "Salary Invoices",colors = "Division")  +
  scale_y_continuous(limits = c(0,31), expand = c(0,NA), breaks = seq(0,31,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Casual Labour Invoices: Percentage Submitted on  time, Percentage Payment Collected on time

```{r Casual Percentage, echo=FALSE, message=FALSE, warning=FALSE}
### Percentage Submitted on Time
IT_CL %>% group_by(Invoice_Recepient,Month) %>% 
  mutate(Submit_On_time = Date_Submitted <= dmy(paste(15,match(Month,month.name),2020)),
         Pay_On_time = Date_Payment_Recieved <= dmy(paste(15,match(Month,month.name),2020))) %>% 
  summarise(Average_Date_Pay = as.integer(mean(day(Date_Payment_Recieved))),
            Average_Date_Submit = as.integer(mean(day(Date_Submitted))),
            Submit_On_time = mean(Submit_On_time) * 100, Pay_On_time = mean(Pay_On_time) * 100) %>% 
  mutate(OPCO = if_else(str_detect(Invoice_Recepient, "^T"),"2B",
                        if_else(str_detect(Invoice_Recepient,"SHPOC"),"SHPOC",Invoice_Recepient))) %>% 
  group_by(OPCO,Month) %>%
  gather(key = "KPI", value = "Score", Average_Date_Pay:Pay_On_time) %>%
  filter(OPCO == "2B") %>% arrange(Invoice_Recepient, .by_group = TRUE) %>%
  mutate(KPI = if_else(KPI == "Average_Date_Pay","Average Date Salary Payment Recieved",
                       if_else(KPI == "Average_Date_Submit","Average Date Salary Invoices submitted on",
                               if_else(KPI == "Submit_On_time" ,"Salary Invoices submitted on time", "Salary Payments Submitted on time"))),
         Invoice_Recepient = if_else(Invoice_Recepient == "TAn4_FIELD", "2A&4 - Field",
                                     if_else(Invoice_Recepient == "TAn4_KRT","2A&4 - KRT",
                                             if_else(Invoice_Recepient == "TB_KRT","2B - KRT","2B - Field")))) %>% 
  ungroup() %>%
  filter(str_detect(KPI,"on time")) %>% 
  select(Month,Invoice_Recepient,KPI,Score, -OPCO) %>% mutate(Month = match(Month,month.name), Score = cummean(Score)) %>% 
  ggplot(aes(Month,Score,color = Invoice_Recepient)) + geom_point() + facet_wrap(~KPI, nrow = 2, ncol = 2) + labs(y = "Percentage Submitted On Time", title = "Salary Invoices", color = "Division")  +
  scale_y_continuous(limits = c(0,100), expand = c(0,NA), breaks = seq(0,100,5)) + scale_x_continuous(labels = month.abb[4:12], breaks = 4:12) + 
  theme(plot.title = element_text(hjust = 0.5))
```

## Customer Service Survey

```{r CSS Details}
CSS %>%  group_by(Dimension,OPCO) %>% summarise(Score = mean(Score) * 25) %>% mutate(KPI = Dimension, Quarter = "3rd")  %>% ungroup() %>% filter(OPCO == "2B") %>%
  select(Quarter, KPI, Score)  %>% kable()
```

## Time Sheets

